\begin{abstract}
    This work uses a data-driven approach to analyse how the resource
    requirements of a population of COPD patients in the South Wales area may
    change, and quantifies how those changes affect the strains of the hospital
    system the population interacts with. This is done using a novel combination
    of often distinct modes of analysis: segmentation, operational queuing
    theory, and the recovery of queuing parameters from incomplete data. By
    combining these methods as presented here, it is demonstrated how the
    potential limitations around the availability of fine-grained data can be
    overcome in operational research. That is, despite only using administrative
    hospital spell data, useful operational results are found.

    The paper begins by finding an effective clustering of the population from
    this granular data that feeds into a multi-class \(M/M/c\) model, the
    parameters of which are recovered from the available data via a 
    parameterisation and the Wasserstein distance. This model is then used to
    conduct a substantial and informative analysis of the underlying queuing
    system and the needs of the population under study through the simulation of
    several `what-if' scenarios.

    The particular set of analyses used to form and study this model
    considers, in effect, all types of patient arrivals as well as how those types
    each impact the system. With that, this study finds that there are no quick
    solutions to reduce the impact of COPD patients on the system, including
    adding capacity to the system. In fact, the only effective intervention to
    reduce the strains of the COPD population is to enact some external policy
    that directly improves the overall health of the COPD population before
    arriving at the hospital.
\end{abstract}
